---
title: "Hello R"
author: "JaMyreion Jackson"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 8
    fig_height: 6
    highlight: espresso
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns. This data frame includes the variables dataset, x, and y.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

First let's plot the data in the circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

First let's plot the data in the all datasets:

```{r plot-dataset}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
 geom_point() +
 facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
 theme(legend.position = "none")
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dataset}
datasaurus_dozen %>%
 group_by(dataset) %>%
 summarize(r = cor(x, y)) %>%
 print(13)
 
## `summarise()` ungrouping output (override with `.groups` argument)
## # A tibble: 13 x 2
##    dataset           r
##    <chr>         <dbl>
## 1 away-0.0641
## 2 bullseye-0.0686
## 3 circle-0.0683
## 4 dino
## 5 dots
## 6 h_lines-0.0645-0.0603-0.0617
## 7 high_lines-0.0685
## 8 slant_down-0.0690
## 9 slant_up-0.0686
## 10 star-0.0630
## 11 v_lines-0.0694
## 12 wide_lines-0.0666
## 13 x_shape-0.0656
```